Check links between old and new pages

### 2023-03-04 src/check_links.Rmd
Update 2013 pages

```{r read_html}
html_path <- "c:/Users/steve/Dropbox/professional/fun stuff/update-website/"
html_path <- "c:/Users/simons/Dropbox/professional/fun stuff/update-website/"
subdir_list=c("99", paste0("0", 0:9), 10:22)
html_files <- NULL
for (yr in subdir_list) {
  file_path <- paste0(html_path, yr)
  list.files(file_path, pattern="html$") -> yr_files
  if (length(yr_files)==0) next
  html_files <- bind_rows(
    data.frame(yr=yr, fn=yr_files),
    html_files)
}
count(html_files, yr)
```

@@

```{r md_links}
sim1 <- "[sim1]: http://www.pmean.com/"
full_file_name <- paste0(md_path, md_files$yr, "/", md_files$fn)
md_links <- NULL
for (i_fn in full_file_name) {
  read_lines(i_fn) %>%
    str_subset(fixed(sim1)) %>%
    str_replace(fixed(sim1), "") -> md_link
  md_link <- ifelse(length(md_link>0), md_link[1], "No link")
  md_file <- str_replace(i_fn, md_path, "")
  md_year <- str_sub(md_file, 1, 2)
  md_file <- str_sub(md_file, 4)
  md_links <- bind_rows(md_links, data.frame(md_year, md_file, md_link))
}

>>>>

```{r read_html}
path_prefix <- "c:/Users"
path_suffix <- "dropbox/professional/fun stuff/update-website"

list.files(path_prefix) %>%
  str_subset("(Simons)|(steve)") -> me

full_path <- glue("{path_prefix}/{me}/{path_suffix}")

print(glue("Searching in {full_path}"))

list.files(full_path)

subdir_list=c("99", paste0("0", 0:9), 10:22)
html_files <- NULL
for (yr in subdir_list) {
  file_path <- glue("{full_path}/{yr}")
  list.files(file_path, pattern="html$") -> yr_files
  if (length(yr_files)==0) next
  html_files <- bind_rows(
    data.frame(yr=yr, fn=yr_files),
    html_files)
}
count(html_files, yr)
```

@@

```{r md_links}
sim1 <- "[sim1]: http://www.pmean.com/"
full_file_name <- glue("{full_path}/{md_files$yr}/{md_files$fn}")
md_links <- NULL
for (i_fn in full_file_name) {
  read_lines(i_fn) %>%
    str_subset(fixed(sim1)) %>%
    str_replace(fixed(sim1), "") -> md_link
  md_link <- ifelse(length(md_link>0), md_link[1], "No link")
  md_file <- str_replace(i_fn, md_path, "")
  md_year <- str_sub(md_file, 1, 2)
  md_file <- str_sub(md_file, 4)
  md_links <- bind_rows(md_links, data.frame(md_year, md_file, md_link))
}
